Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-17 ms.tex
still cleaning up discussion of fits with variable f1

As mentioned in $\S$\ref{sec:modeling}, the combination of high S/N and high 
angular resolution afforded by the \PLANCK~HFI maps provides us with the 
opportunity to allow additional parameters of the two-component model, 
previously fixed by FDS99, to vary spatially. Specifically, we consider
allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
spatially constant. In principle, we could alternatively introduce a third free
 parameter by allowing $q_1/q_2$, $\beta_1$ or $\beta_2$ to vary while holding 
$f_1$ fixed. However, a model in which $f_1$ varies continuously from one line 
of sight to another is the most natural three-parameter scenario, in that $f_1$
variation can be attributed to continuous variation of the dust species' mass
fractions, whereas continuous variations in the other global parameters, which 
represent grain emission/absoprtion properties, seem less plausible.

% sentence or two about why f_1 is natural parameter to try varying 
% rather than q1/q2 or beta1 or beta2 !!!!!~~!!!

In order for our variable $f_1$ fits to remain sufficiently constrained with 
the addition of another free parameter, we consider \PLANCK~maps smoothed to 
$1^{\circ}$ FWHM for increased S/N, and pixelize at $N_{side}=64$. To best
constrain the model parameters in each pixel, we also include \PLANCK~100 GHz 
and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ resolution.

We run the Markov chains in three dimensions sampling in all three of $f_1$,
$\tilde{I}_{545}$ and $T_2$. We are now sampling the posterior given by:

@@

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only nine intensity measurements, several of which are quite noisy. 
%To boost S/N, we have performed
%the fits using maps smoothed to $1^{\circ}$ resolution.

>>>>

As mentioned in $\S$\ref{sec:modeling}, the combination of high S/N and high 
angular resolution afforded by the \PLANCK~HFI maps provides us with the 
opportunity to allow additional parameters of the two-component model, 
previously fixed by FDS99, to vary spatially. Specifically, we consider
allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
spatially constant. In principle, we could alternatively introduce a third free
parameter by permitting $\beta_1$, $\beta_2$ or $q_1/q_2$ to vary while holding
$f_1$ fixed. However, a model in which $f_1$ varies continuously from one line 
of sight to another is the most natural three-parameter scenario, in that $f_1$
variation can be attributed to continuous changes in the dust species' mass
fractions, whereas continuous variations in the other global parameters, which 
represent grain emission/absoprtion properties, seem less plausible.

In order for our variable $f_1$ fits to remain sufficiently constrained 
following the introduction of a third free parameter, we enhance per-pixel S/N 
by smoothing the input maps $1^{\circ}$ FWHM, and pixelize at $N_{side}=64$. To
best constrain the model parameters in each pixel, we also include \PLANCK~100 
GHz and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ 
resolution.

We now run Markov chains sampling in all three of $f_1$, $\tilde{I}_{545}$ and 
$T_2$, with the posterior given by:

@@

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only nine intensity measurements, several of which are quite noisy.
